### 2021-04-20 conclusion.tex
conclusion typos

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help designing new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these pattern to a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}

@@

The same applies to the idea of learning to recommend 
both the predicate and the function precedences using a single \gls{gcn}.
The joint learning, although more complex to design, could 
additionally discover interdependencies
between the effects of the function precedence and predicate precedence on the proof search,
while the current setup implicitly assumes that the effects are independent.
Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
in one training batch.

>>>>

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help designing new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these patterns to a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}

@@

The same applies to the idea of learning to recommend 
both the predicate and the function precedences using a single \gls{gcn}.
The joint learning, although more complex to design, could 
additionally discover interdependencies
between the effects of the function precedence and predicate precedence on the proof search,
while the current setup implicitly assumes that the effects are independent.
Finally, a higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
in one training batch.
